A sheaf--function dictionary for algebraic tori over local fields

### 2013-08-19 shanghai.tex
Fixed a few typos.
Moving to a different computer.

In Part 2 we use Theorem~\ref{thm:snake} to make a sheaf--function dictionary
for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_n$ be the
Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
allows us to translate characters $T(K)$ of depth less than $d$ into quasicharacter sheaves on $\GN{T}_d$:
\[
\QCiso{\GN{T}_n} 
\iso
\Hom_{< n}(T(K),\EEx).
\]  
We refer to finite-depth characters of $T(K)$ as quasicharacters and
describe a group scheme $\GN{T}$ simultaneously geometrizing all such quasicharacters.

@@

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{deligne:SGA4.5}, \David{more specific citation} and more recently Drinfeld has referred to such objects
as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
is a direct generalization of the sheaf--function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The main use
of the term ``character sheaf'' is due to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
handling non-commutative groups; though he does define character sheaves for some
non-connected groups he restricts his attention to reductive groups with cyclic component group, which are extensions of $\ZZ/n\ZZ$ by a torus. 
In this case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.

@@

As Proposition~\ref{prop:connected} shows, 
when $G$ is a connected algebraic group over $\Fq$, 
it is appropriate to replace quasicharacter sheaves on $G$ 
with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$. 
In this context, finite quasicharacter sheaves may also be apprehended as
\emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
As explained in \cite{kamgarpour:09a}*{\S~2}, 
the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
that factor through a particular quotient of $\pi_1(G,{\bar e})$ 
denoted there by $\Pi_\text{disc}(G)$.
%\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
From this it is apparent that the category of discrete isogenies to $G$ is a Galois category,
in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$,
as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.

@@

With Theorem~\ref{thm:snake} on hand, 
we can see why neither bounded quasicharacter sheaves 
nor finite quasicharacter sheaves are up to the task of 
geometrizing characters of $G(\Fq)$ in the generality we need.  
%
Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$. 
Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}. 
Then $\trFrob{\qcs{L}}(1) = \ell$. Suppose $\qcs{L}$ was a bounded quasicharacter sheaf. 
Then the restriction of $\qcs{L}$ to the connected component $1\in G$ 
would be a $\ell$-adic local system on $1$ of rank-1, 
thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
$\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
So the Weil sheaf $\gqcs{L}$ does not descend to a local system on $G$.
It follows that the quasicharacter sheaf $\qcs{L}$ is not a bounded quasicharacter sheaf.
%
We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded,
defined at $1$ by a pro-\'etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
%
These simple examples illustrate why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.

@@

We will also need the Greenberg functor, 
introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
as a functor from the category of schemes locally of finite type 
over an Artinian local ring with perfect residue field $k$ 
to the category of schemes locally of finite type over $k$. 
This functor respects open immersions, closed immersions, 
etale morphisms and smooth morphisms. 
Besides Greenberg's original papers, 
see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
and the first few sections of \cite{stasinski:12a} 
for background on the Greenberg functor.

For any positive integer $n$, let
\[
%\begin{tikzcd}
\Gr_n : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
%\end{tikzcd}
\]
be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ 
%\Clifton{Do you think I should say more about $P_{n}$?}
\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
For a given Néron model $\TT$ of $T$, set
\[
\GN{T}_n \ceq \Gr_n(\TT)
\qquad \text{and}\qquad
f_n \ceq P_n(\TT).
\]
%
\Clifton{I guess this next bit needs to be re-structured.}
Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
 \begin{enumerate}
   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
  \labitem{(GN.1)}{smooth} $\GN{T}_n$ is a smooth commutative group scheme
  locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
  geometrically finitely generated: $\underline{T}$ is a smooth group scheme over $\OK$, by construction; since smoothness is preserved under base change, $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ is a smooth group scheme over an Artinian ring with perfect residue field; the Greenberg functor preserves smoothness, so $\GN{T}_n$ is a smooth group scheme over $\Fq$; the identity component of any smooth group scheme is geometrically connected, hence connected, and the Greenberg functor takes the geometric identity component of $\TT_n$ to the geometric identity component of $\GN{T}_n$;
  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
  this group is finitely generated by \cite{xarles:93a}*{2.18}.
  \labitem{(GN.2)}{truncation}
  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes. To see this, it suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$. Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes). Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$. 
\Clifton{I still need to confirm this claim.}
Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
  \end{enumerate}
%
We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.

@@

For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!! 
What's the covering group of $f_{n\leq m}$? 
Must be the finite group $\GN{T}_{m}(\Fq)/\GN{T}_n(\Fq)$, which could be $\TT^0(\pK^n/\pK^{m})$. 
We might be able to build some very special finite quasicharacter sheaves on $\GN{T}_n$ this way.}
Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
%
%\begin{proposition}\label{prop:nm}
The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful, by \ref{truncation}.
%\end{proposition}
%
%\begin{proof}
%
%\end{proof}

@@

\begin{proof}
Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
\[
\begin{tikzcd}
\ & & & \QC(\GN{T})\\
\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & \\
\end{tikzcd}
\]
defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
Passing to isomorphism classes of objects, we get 
\[
\begin{tikzcd}
\ & & & & \QCiso{\GN{T}}\\
\ & & & \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \arrow{ur}{\exists ! \theta} & \\
\arrow{urrr}{F_n} \QCiso{\GN{T}_n} \arrow[swap]{rr}{f_{n\leq m}^*} && \QCiso{\GN{T}_m} \arrow[swap]{ur}{F_m} & & \\
\end{tikzcd}
\]
The group homomorphism 
$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$ is a bijection 
with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
Now use Theorem~\ref{thm:application}.
\end{proof}

\Clifton{Make comments here about the depth-preserving isomorphism  . .  .}

@@

This paper has shown how quasicharacter sheaves 
on the Greenberg transform of the N\/eron model of $T$ 
determine admissible characters of $T(K)$, and vice versa, functorially.
When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
which enjoys the same functorial properties, 
it follows that quasicharacter sheaves for $T$ 
determine Langlands parameters for $T$, and vice versa, functorially.
\[
\begin{tikzcd}
\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
\end{tikzcd}
\]
We suspect that it is possible to extract Langlands parameters 
from quasicharacter sheaves directly and that the reciprocity map 
can then be be viewed as pairing characters and parameters coming
 from the same quasicharacter sheaf. 
 Results in this paper provide some tools for reduction of the problem to the case $T=\Gm{K}$. 
 In that case, our suspicions are all but confirmed 
 by the class field theory of Serre-Hazewinkel
 \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
 especially as revisited in \cite{suzuki-yoshida:12a}*{\S~2}. 
 What remains to be done is a careful comparison of 
 quasicharacter sheaves for $\Gm{K}$ and certain local systems on
  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{suzuki-yoshida:12a}.

>>>>

In Part 2 we use Theorem~\ref{thm:snake} to make a sheaf--function dictionary
for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
$\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
allows us to translate characters $T(K)$ of depth less than $d$ into quasicharacter sheaves on $\GN{T}_d$:
\[
\QCiso{\GN{T}_n} 
\iso
\Hom_{< n}(T(K),\EEx).
\]  
We refer to finite-depth characters of $T(K)$ as quasicharacters and
describe a group scheme $\GN{T}$ simultaneously geometrizing all such quasicharacters.

@@

We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
Analogous sheaves on connected, commutative algebraic groups were first studied
by Deligne \cite{deligne:SGA4.5}, \David{more specific citation} and more recently Drinfeld has referred to such objects
as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
is a direct generalization of the sheaf--function dictionary to the case of commutative
group schemes which are not necessarily connected or finite type.  The main use
of the term ``character sheaf'' is due to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
handling non-commutative groups; though he does define character sheaves for some
non-connected groups he restricts his attention to reductive groups with cyclic component group. If commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
in which case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.

@@

As Proposition~\ref{prop:connected} shows, 
when $G$ is a connected algebraic group over $\Fq$, 
it is appropriate to replace quasicharacter sheaves on $G$ 
with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$. 
In this context, finite quasicharacter sheaves may also be apprehended as
\emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
As explained in \cite{kamgarpour:09a}*{\S~2}, 
the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
that factor through a particular quotient of $\pi_1(G,{\bar e})$ 
denoted there by $\Pi_\text{disc}(G)$.
%\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
From this it is apparent that the category of discrete isogenies to $G$ is a Galois category,
in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$,
as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.

@@

With Theorem~\ref{thm:snake} in hand, 
we can see why neither bounded quasicharacter sheaves 
nor finite quasicharacter sheaves are up to the task of 
geometrizing characters of $G(\Fq)$ in the generality we need.  
%
Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$. 
Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}. 
Then $\trFrob{\qcs{L}}(1) = \ell$. Suppose $\qcs{L}$ was a bounded quasicharacter sheaf. 
Then the restriction of $\qcs{L}$ to the connected component $1\in G$ 
would be a $\ell$-adic local system on $1$ of rank-1, 
thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
$\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
So the Weil sheaf $\gqcs{L}$ does not descend to a local system on $G$.
It follows that the quasicharacter sheaf $\qcs{L}$ is not a bounded quasicharacter sheaf.
%
We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded,
defined at $1$ by a pro-\'etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
%
These simple examples illustrate why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.

@@

We will also need the Greenberg functor, 
introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
as a functor from the category of schemes locally of finite type 
over an Artinian local ring with perfect residue field $k$ 
to the category of schemes locally of finite type over $k$. 
This functor respects open immersions, closed immersions, 
etale morphisms, smooth morphisms and geometric components.
Besides Greenberg's original papers, 
see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
and the first few sections of \cite{stasinski:12a} 
for background on the Greenberg functor.

For any positive integer $n$, let
\[
%\begin{tikzcd}
\Gr_n : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
%\end{tikzcd}
\]
be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ 
%\Clifton{Do you think I should say more about $P_{n}$?}
\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
For a given Néron model $\TT$ of $T$, set
\[
\GN{T}_n \ceq \Gr_n(\TT)
\qquad \text{and}\qquad
f_n \ceq P_n(\TT).
\]
%
\Clifton{I guess this next bit needs to be re-structured.}
Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
 \begin{enumerate}
   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
  \labitem{(GN.1)}{smooth} $\GN{T}_n$ is a smooth commutative group scheme
  locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
  geometrically finitely generated: $\underline{T}$ is a smooth group scheme over $\OK$, by construction; since smoothness is preserved under base change, $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ is a smooth group scheme over an Artinian ring with perfect residue field; the Greenberg functor preserves smoothness, so $\GN{T}_n$ is a smooth group scheme over $\Fq$; the identity component of any smooth group scheme is geometrically connected, hence connected, and the Greenberg functor takes the geometric identity component of $\TT_n$ to the geometric identity component of $\GN{T}_n$;
  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
  this group is finitely generated by \cite{xarles:93a}*{2.18}.
  \labitem{(GN.2)}{truncation}
  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes. To see this, it suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$. Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes). Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$. 
\Clifton{I'm working on this.}
Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
  \end{enumerate}
%
We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.

@@

For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
%\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!!  What's the covering group of $f_{n\leq m}$?  Must be the finite group $\GN{T}_{m}(\Fq)/\GN{T}_n(\Fq)$, which could be $\TT^0(\pK^n/\pK^{m})$. We might be able to build some very special finite quasicharacter sheaves on $\GN{T}_n$ this way.}
Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
%
%\begin{proposition}\label{prop:nm}
The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful, by \ref{truncation}.
%\end{proposition}
%
%\begin{proof}
%
%\end{proof}

@@

\begin{proof}
Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
\[
\begin{tikzcd}
\ & & & \QC(\GN{T})\\
\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & \\
\end{tikzcd}
\]
defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
Passing to isomorphism classes of objects and invoking the universal property of $\varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d}$ gives a group homomorphism
$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$; this is a bijection 
with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
Now use Theorem~\ref{thm:application}.
\end{proof}

@@

This paper has shown how quasicharacter sheaves 
on the Greenberg transform of the N\/eron model of $T$ 
determine admissible characters of $T(K)$, and vice versa, functorially.
When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
which enjoys the same functorial properties, 
it follows that quasicharacter sheaves for $T$ 
determine Langlands parameters for $T$, and vice versa, functorially.
\[
\begin{tikzcd}
\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
\end{tikzcd}
\]
We suspect that it is possible to extract Langlands parameters 
from quasicharacter sheaves directly and that the reciprocity map 
can then be be viewed as a matching between quasicharacters and Langlands parameters coming
 from the same quasicharacter sheaf. 
 Results in this paper provide some tools for reduction of the problem to the case $T=\Gm{K}$. 
 In that case, our suspicions are all but confirmed 
 by the class field theory of Serre-Hazewinkel
 \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
 especially as revisited in \cite{suzuki-yoshida:12a}*{\S~2}. 
 What remains to be done is a careful comparison of 
 quasicharacter sheaves for $\Gm{K}$ and certain local systems on
  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{suzuki-yoshida:12a}.
